Cryptanalysis of \MORUS

### 2018-05-11 morusAC.tex
Page numbers
working on introduction
Conclusion
Some more copyediting
rollback for Tomer
ePrint version: author names + acknowledgments + increased margins

\newif\ifanonymous
%\anonymoustrue%uncomment for submission version

\newif\ifshrink\shrinkfalse
%\shrinktrue for screen-friendly original LNCS paper size

\documentclass[a4paper]{llncs}
\usepackage{common}

\ifanonymous
\author{}
\institute{}
\else
\author{Tomer Ashur \and Maria Eichlseder \and Ga\"etan Leurent \and Brice Minaud \and Yann Rotella \and Yu Sasaki \and Beno\^it Viguier}
\institute{}
%\path|tomer.ashur@esat.kuleuven.be|, \path|maria.eichlseder@iaik.tugraz.at|, \path|gaetan.leurent@inria.fr|, \path|brice.minaud@gmail.com|, \path|yann.rotella@inria.fr|, \path|b.viguier@science.ru.nl|, \path|sasaki.yu@lab.ntt.co.jp|
\fi

@@

\title{\morus: Biases in the Stream}
\maketitle
\todo{The title should reflect the full analysis. How about something more generic?}

\input{morusAC_00_Abstract}
\input{morusAC_01_Introduction}
\input{morusAC_02_Preliminaries}
\input{morusAC_03_MiniMorus}
\input{morusAC_04_Mini_trails}
\input{morusAC_05_Full_trails}
\input{morusAC_06_Discussion}
\input{morusAC_07_IniFin}

@@

>>>>

\newif\ifanonymous
\newif\iflncsmargins
%\anonymoustrue%uncomment for submission version

\newif\ifshrink
%\shrinktrue % for screen-friendly original LNCS paper size

\documentclass[a4paper]{llncs}
\usepackage{common}
\pagestyle{plain}
\usepackage{multirow}

\ifanonymous
\lncsmarginstrue
\author{}
\institute{}
\else
\author{Tomer Ashur\inst{1} \and Maria Eichlseder\inst{2} \and Martin M. Lauridsen \and Ga\"etan Leurent\inst{3} \and Brice Minaud\inst{4} \and\\ Yann Rotella\inst{3} \and Yu Sasaki\inst{5} \and Beno\^it Viguier\inst{6}}
\institute{
imec-COSIC KULeuven, Belgium
\and
Graz University of Technology, Austria
\and
Inria, France
\and
Royal Holloway, University of London, United Kingdom
\and
NTT, Japan
\and
Radboud University, Netherlands\\
\path|tomer.ashur@esat.kuleuven.be|, \path|maria.eichlseder@iaik.tugraz.at|, \path|mail@martinlauridsen.info|, \path|gaetan.leurent@inria.fr|, \path|brice.minaud@gmail.com|, \path|yann.rotella@inria.fr|, \path|b.viguier@science.ru.nl|, \path|sasaki.yu@lab.ntt.co.jp|
}
\fi

\iflncsmargins
\else
\usepackage[hmargin=2.5cm,vmargin=3cm]{geometry}
\fi

@@

\title{Cryptanalysis of \MORUS}
\maketitle
\thispagestyle{plain}

\input{morusAC_00_Abstract}
\input{morusAC_01_Introduction}
\input{morusAC_02_Preliminaries}
\input{morusAC_03_MiniMorus}
\input{morusAC_04_Mini_trails}
\input{morusAC_05_Full_trails}
\input{morusAC_06_Discussion}
\input{morusAC_07_IniFin}
\input{morusAC_08_Conclusion}

@@

%\section*{Auxiliary Material}
\clearpage
